Profit Optimisation in Heterogeneous 2-link Parallel Games

### 2025-01-04 thesis/article.tex
Thesis: Finished Future Work and Appendix (with all unused propositions included)

\thispagestyle{empty}
\pagenumbering{gobble}
\chapter*{Συνοψη}
Σε αυτή τη διπλωματική μεταπτυχιακού μελετάμε ένα παίγνιο $2$ επιπέδων όπου, σε ένα δίκτυο με $n$ ακμές από μια πηγή $s$ σε ένα στόχο $t$, μια μονάδα ροής θέλει να μετακινηθεί από το $s$ στο $t$ χρησιμοποιώντας την ακμή με το χαμηλότερο κόστος, ενώ οι διαχειριστές των ακμών ανταγωνίζονται για κέρδος βάζοντας δίοδια στις ακμές και δημιουργώντας έτσι ένα παίγνιο συμφόρησης με διόδια.
Εξετάζουμε μόνο αφινικές καθυστερήσεις για τις ακμές.
Επιπλέον, ο κάθε χρήστης δικτύου αντιδρά στα διόδια με ετερογενή τρόπο, δηλ. ο κάθε παίκτης $p$ στη ροή του δικτύου έχει διαφορετική τιμή ευαισθησίας χρόνου-χρήματος, η οποία περιγράφεται από μια συνάρτηση κατανομής $\alpha(p)$.
Πρώτα παρουσιάζουμε κάποιους βασικούς ορισμούς και ιδιότητες των ομογενών παιγνίων κέρδους, κυρίως βασισμένα σε προηγούμενες δουλειές, και με αυτά ως βάση, τα επεκτείνουμε για να περιγράψουμε παίγνια κέρδους με ετερογενείς χρήστες.
Εισαγάγουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού ευαισθησίας $\as(t)$, ορισμένη για οποιεσδήποτε $2$ ακμές του δικτύου ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία, δωσμένων σετ διοδίων $t$, τα κόστη των $2$ ακμών είναι ίσα.
Με τη βοήθεια της $\as$ θα περιγράψουμε μερικές ιδιότητες γύρω από την εγωιστική συμπεριφορά των ετερογενών χρηστών για διαφορετικά διόδια, καθώς και θα αποδείξουμε την ύπαρξη άνω φράγματος για τις τιμές ευαισθησίας που αφορούν το παίγνιο.
Στη συνέχεια, φτάνοντας στο κύριο σώμα αυτής της έρευνας, εξετάζουμε την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών για διαφορετικές περιπτώσεις ετερογενών χρηστών.
Δείχνουμε ότι δεν υπάρχει ισορροπία Nash όταν υπάρχουν πολλοί χρήστες με $0$ ευαισθησία, δηλ. παίκτες που δεν επηρρεάζονται από τα διόδια, οπότε στο εξής υποθέτουμε ότι $\alpha(p) > 0$.
Κατόπιν εξετάζουμε περιπτώσεις όπου η συνάρτηση κατανομής είναι σταθερή, η οποίες, αν και δημιουργούν ομογενή συμπεριφορά στους χρήστες (κάνοντάς τα ψευδο-ετερογενή παίγνια), μας βοηθάνε να περιγράψουμε πώς συμπεριφέρονται η ροή, τα διόδια και τα σημεία ισορροπίας όταν αυτή η σταθερή τιμή μεταβάλλεται.
Χρησιμοποιώντας όλα τα παραπάνω, μελετάμε βηματικές συναρτήσεις κατανομής, όπου περιορίζοντας το μοντέλο μας σε στιγμιότυπα $2$ ακμών, παρουσιάζουμε αυστηρές συνθήκες αναγκαίες για την ύπαρξη ή μη σημείου ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών.
Παρουσιάζουμε και αναλύουμε έναν αλγόριθμο για τον υπολογισμό του σημείου ισορροπίας, αν υπάρχει, και κλείνουμε με μια συζήτηση για πιθανή μελοντική δουλειά.

@@

Acemoglu and Ozdaglar were the first to introduce pricing competition between link operators to the above model \cite{10.1287/moor.1060.0231}.
They showed that increasing the competition among operators from a monopoly to an oligopoly may reduce the efficiency of the network, achieving tight bounds on the Price of Anarchy.
In a follow-up work \cite{10.1109/JSAC.2007.070812}, they generalised the above by assuming more general topologies where links can also be linked serially (series-parallel networks).
Correa et al. \cite{correa2018pricing} showed pricing games may not exist, may not be unique and can be arbitrarily inefficient, but regulating the network with toll caps can solve all three issues.
Harkes et al. \cite{Harks_2019} then showed that the same is true for uniform toll caps, which is stronger in practice as toll discrimination is often not allowed.
The latter two papers have also been main pillars of the current work.

@@

In this chapter we will introduce the pricing competition game to our model and examine how different distribution functions can affect the profit maximisation game between the toll operators.
We will begin by noticing that players with no toll fear, i.e. $\alpha(p)$ close to $0$, can be exploited by some link operators who then get unbounded profits (Lemma \ref{lemma:a_0_0}).
This obviously breaks the pricing competition game and, in turn, leads us to include the restriction of $\alpha(p) > 0$ when $p > 0$.
We will then proceed to analyse games with fixed distribution functions, where in Lemma \ref{lemma:a_fixed_homogeneous} we will show that such games are, as intuition suggests, equivalent to homogeneous games.
Special interest will then be on comparing such games, specifically those with the same setup but different fixed $\alpha$ functions, as Lemma \ref{lemma:a_fixed_c_relation} will reveal that uniformly varying the player sensitivity maps the toll values around the same flow.
The tools and notions built above will prove extremely useful when we next analyse games with step distribution functions, where we'll restrict our analysis to instances with $2$ links to simplify our work.
For those we will show an equivalence with a homogeneous game for a given toll \ref{lemma:heterogenous_flow_equiv_fixed} and combining it with Lemma \ref{lemma:alpha_step_gaps} where we'll show that a Nash Equilibrium cannot exist with all players of each sensitivity type using a single link, we get this chapter's main result, Theorem \ref{theorem:a_step_ne_equiv_fixed}, which states that if a Nash Equilibrium exists in a heterogeneous game with a step distribution function, then the respective homogeneous also has an equilibrium for the same set of tolls.
Using this notion, we will describe an algorithm (\ref{algorithm:ne_pricing}) which can decide existence and return the Nash Equilibrium for the pricing competition game in a heterogeneous $2$-link network.

@@

What we need to examine  next is how those two games react differently for an link $i$ given a fixed $t_{-i}$.
For this it is important to focus again on the fact that the flow is exclusively dependent on the toll difference.

TODO: Fix the next Lemma.
For affine latencies, we can calculate the best response functions $B_i(t_{-i})$.
For each link operator $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
\begin{equation}
	\label{eq:homogeneous_br_i}
	B_i(t_{-i}) = \frac{1 + \sum_{j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \ne i}\frac{2}{a_j}}
\end{equation}

%In the extreme cases where the toll differences are arbitrarily large, the best response of some players will be to lower their toll and take all available flow.

To describe more properties of homogeneous pricing games we will need the following crucial Lemma.
\begin{lemma}
	\label{lemma:tolls_diff}
	Let $(N, \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$, a vector of $t_i - t_j$ values for all $t_j \in t_{-i}$.
	Then $D_i$ is decreasing with regard to any $t_j \in t_{-i}$.
\end{lemma}

\begin{proof}
	For any link $i$ and any $t_j \in t_{-i}$ consider the respective element of $D_i$, which is $B_i(t_{-i}) - t_j$.
	From formula \ref{eq:homogeneous_br_i} after some calculations we get
	\[
	B_i(t_{-i}) - t_j = \left(\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1\right)t_j + \frac{1 + \frac{b_j - b_i}{a_j} + \sum_{k \ne i, j}\frac{b_k + t_k - b_i}{a_k}}{\sum_{k \ne i} \frac{2}{a_k}}
	\]
	which is decreasing with regards to $t_j$ if and only if its coefficient is negative.
	Indeed, since $a_i > 0$ for all $i$, we get
	\[
	\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1 = \frac{1}{2 \left(1 + \sum_{k \ne i, j} \frac{a_j}{a_k}\right)} - 1 \leq \frac{1}{2} - 1 < 0
	\]
\end{proof}

\begin{lemma}
	\label{lemma:a_fixed_t_iM_fixed}
	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
	Also let $t_{-i_M}^{(1)}, t_{-i_M}^{(2)}$ the smallest possible $t_{-i}$ where $x_i(B_i(t_{-i}), t_{-i}) = 1$, respectively for each game.
	Then the following hold.
	\begin{enumerate}[$(i)$]
		\item $t_{-i_M}^{(2)} < t_{-i_M}^{(1)}$
		\item $x_i^{(1)}(B_i^{(1)}(0), 0) = x_i^{(2)}(B_i^{(2)}(0), 0)$
		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) = x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i}) = 1$ for all $t_{-i} \ge t_{-i_M}^{(1)}$
		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) < x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})$, for all $t_{-i} \in (0, t_{-i_M}^{(1)})$
		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}), x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})$ get max distance at $t_{-i_M}^{(2)}$ \\
		\textit{(conjecture)}
	\end{enumerate}
\end{lemma}

\begin{proof}
	$ $
	\begin{enumerate}[$(i)$]
		\item Assume $t_{-i_M}^{(2)} \ge t_{-i_M}^{(1)}$.
		Then from Corollary \ref{corollary:a_fixed_c_relation} we get
		\begin{flalign*}
			1 = &x_i^{(1)}(B_i^{(1)}(t_{-i_M}^{(1)}), t_{-i_M}^{(1)}) = x_i^{(2)}\left( \frac{c_1}{c_2} \cdot B_i^{(1)}(t_{-i_M}^{(1)}), \frac{c_1}{c_2} \cdot t_{-i_M}^{(1)}\right) & \\
			&= x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i_M}^{(1)}\right), \frac{c_1}{c_2} \cdot t_{-i_M}^{(1)}\right) &
		\end{flalign*}
		which is a contradiction since $\frac{c_1}{c_2} t_{-i_M}^{(1)} < t_{-i_M}^{(1)} \le t_{-i_M}^{(2)}$ and $t_{-i_M}^{(2)}$ is the smallest value with that property.
		Therefore the initial assumption is wrong and we get $t_{-i_M}^{(2)} < t_{-i_M}^{(1)}$.
		\item With application of Corollary \ref{corollary:a_fixed_c_relation} we have
		\[
			x_i^{(1)}(B_i^{(1)}(0), 0) = x_i^{(2)}\left(\frac{c_1}{c_2} \cdot B_i^{(1)}(0), 0\right) = x_i^{(2)}(B_i^{(2)}(0), 0)
		\]
		\item Since from $(i)$ we have $t_{-i_M}^{(1)} = \max\{t_{-i_M}^{(1)}, t_{-i_M}^{(2)}\}$ then the property follows from the definitions of $t_{-i_M}^{(1)}, t_{-i_M}^{(2)}$.
		\item For $t_{-i} \in (t_{-i_M}^{(2)}, t_{-i_M}^{(1)})$ obviously
		\[
			x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) < 1 = x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})
		\]
		Then for $t_{-i} \in (0, t_{-i_M}^{(2)})$ with the same way we used Corollary \ref{corollary:a_fixed_c_relation} as in $(i)$ we see that
		\[
			x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) = x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right), \frac{c_1}{c_2} \cdot t_{-i}\right)
		\]
		where the second part is the flow in $\Gm_2$ at the best response of link operator $i$ against $\frac{c_1}{c_2} t_{-i}$.
		Therefore their best response against $t_{-i} > \frac{c_1}{c_2} t_{-i}$ will have a lower toll difference to $t_{-i}$ (\ref{lemma:tolls_diff}) and thus more flow, arriving at
		\[
			x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right), \frac{c_1}{c_2} \cdot t_{-i}\right) < x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})
		\]
	\end{enumerate}
\end{proof}

%\begin{lemma}
%	\label{lemma:a_fixed_x12}
%	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
%	Then the following hold.
%	\begin{enumerate}[$(i)$]
%		\item $x^{(1)}(0) = x^{(2)}(0)$
%		\item $x_i^{(1)}(t) - x_i^{(2)}(t)$ is non-decreasing in relation to $t_i - t_{-i}$
%	\end{enumerate}
%\end{lemma}
%Notice that the above Lemma also provides us with $x_i^{(1)}(t) < x_i^{(2)}(t)$ iff $t_i < t_{-i}$ and vice versa, as well as that this difference is expanded as $t_i - t_{-i}$ does.
%We avoided using the affinity of the latency functions on purpose to get a more general notion between the two games.
%Using latency functions now, we can get a calculated version of the above.
%\begin{corollary}
%	\label{lemma:a_fixed_x12_calc}
%	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same affine latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
%	Then for some fixed number $K_i > 0$ it holds that
%	\[x_i^{(1)}(t) - x_i^{(2)}(t) = K_i \cdot (t_i - t_{-i})\]
%\end{corollary}
%
%\begin{proof}
%	From equation \ref{eq:homogeneous_x_i} for $2$ links and under universal sensitivity $c_1, c_2$ respectively we get
%	\begin{align*}
%		x_i^{(1)}(t) - x_i^{(2)}(t) &= \frac{a_{-i} + b_{-i} + c_1t_{-i} - b_i - c_1t_i}{a_i} - \frac{a_{-i} + b_{-i} + c_2t_{-i} - b_i - c_2t_i}{a_i} \\
%		&= \frac{(c_2 - c_1)(t_i - t_{-i})}{a_i}
%	\end{align*}
%	So the property holds for $K_i = \frac{c_2 - c_1}{a_i} > 0$.
%\end{proof}

We finally arrive at the main theorem of this section, which describes similar properties for the relative behaviour of the profit functions between the two games.
Fist, let's remind ourselves that from Lemma \ref{lemma:tolls_diff} for each game $B_i(t_{-i}) - t_{-i}$ is decreasing as well as continuous.
Therefore, given that best responses range from above and below $t_{-i}$ values, there exists some $t_{-i_0}$ for which $B_i(t_{-i_0}) = t_{-i_0}$.
We state now our theorem.

\begin{theorem}
	\label{theorem:a_fixed_t_i0}
	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
	Also let $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ the respective tolls for which $B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)}$ and $B_i^{(1)}(t_{-i_0}^{(2)}) = t_{-i_0}^{(2)}$.
	Then for all links $i$ it holds that
	\begin{enumerate}[$(i)$]
		\item $t_{-i_0}^{(1)} > t_{-i_0}^{(2)}$
		\item There exists $t_{-i_0} \in \left(t_{-i_0}^{(2)}, t_{-i_0}^{(1)}\right)$ such that
		\[\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}) = \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0})\]
		\item $\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$ is non-increasing in relation to $t_{-i}$.
		\item $t_{-i_0}$ is the geometric mean of $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$
	\end{enumerate}
\end{theorem}

\begin{proof}
	$ $
	\begin{enumerate}[$(i)$]
		\item From Corollary \ref{corollary:a_fixed_c_relation}$(iii)$ we get
		\[
			B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)} \Rightarrow B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i_0}^{(1)}\right) = \frac{c_1}{c_2} \cdot t_{-i_0}^{(1)}
		\]
		and from the fact that $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ are the unique solutions of their respective equations we get $t_{-i_0}^{(2)} = \frac{c_1}{c_2} \cdot t_{-i_0}^{(1)} < t_{-i_0}^{(1)}$.
		\item Consider the function $\Pi_i(t_{-i}) = \max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$.
		Then for $t_{-i} = t_{-i_0}^{(2)}$ we see that in $\Gm_2$ the best response for link operator $i$ is to play the same toll as in the other link, therefore they get max profit at $x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$.
		In $\Gm_1$ now, since $t_{-i_0}^{(2)} < t_{-i_0}^{(1)}$ then the best response for link operator $i$ is for some $t_i > t_{-i_0}^{(2)}$, and since from \ref{corollary:a_fixed_c_relation}$(i)$ the profit $x_i^{(1)}(0) = x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$ is also one of their options, it means that the profit at $t_i$ is greater, i.e.
		\[
			\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}^{(2)}) > \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0}^{(2)}) \Rightarrow \Pi_i(t_{-i_0}^{(2)}) > 0
		\]
		Similarly we can show that $\Pi_i(t_{-i_0}^{(1)}) < 0$.
		With all the above and given that we know from the analysis in Harkes et al. \cite{Harks_2019} that best response functions are continuous, from the Bolzano theorem (TODO: Is this the right theorem? Reference?) we get that there exists $t_{-i_0} \in \left(t_{-i_0}^{(2)}, t_{-i_0}^{(1)}\right)$ such that $\Pi_i(t_{-i_0}) = 0$, which gives us the desired proposition.
		\item We will use the same $\Pi_i$ function as in $(ii)$, so we instead need to show that $\Pi_i(t_{-i})$ is non-decreasing in relation to $t_{-i}$.
		For all $t_{-i} \ge t_{-i_M}^{(1)}$ from Lemma \ref{lemma:a_fixed_t_iM_fixed} we get $\Pi_i(t_{-i}) = 1 \cdot B_i^{(1)}(t_{-i}) - 1 \cdot B_i^{(2)}(t_{-i})$, where the best responses have fixed differences to $t_{-i}$ (and therefore to each other as well), making $\Pi_i(t_{-i})$ in turn fixed for all $t_{-i} \ge t_{-i_M}^{(1)}$.
		TODO: Pending.
		\item By using the $B_i(t_{-i})$ formula to find $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ and then solve $\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}) = \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0})$.
		TODO: Either replace with a theoretical proof or write the calculations.
	\end{enumerate}
\end{proof}

Finally, we can again calculate $t_{-i_0}$ using the closed formulas provided by the affine assumption.

\begin{corollary}
	\label{corollary:a_fixed_ti0_calc}
	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
	Then for $t_{-i_0}$ defined in Theorem \ref{theorem:a_fixed_t_i0} for the two games it holds that
	\[t_{-i_0} = \frac{a_{-i} + b_{-i} - b_i}{\sqrt{c_1 c_2}}\]
\end{corollary}

\begin{proof}
	We can easily calculate $t_{-i_0}^{(1)}$ and $t_{-i_0}^{(2)}$.
	For $\Gm_1$ we have
	\[B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)} \Rightarrow \frac{a_{-i} + b_{-i} - b_i + c_1 t_{-i_0}^{(1)}}{2 c_1} = t_{-i_0}^{(1)} \Rightarrow t_{-i_0}^{(1)} = \frac{a_{-i} + b_{-i} - b_i}{c_1}\]
	Similarly for $\Gm_2$ we have $t_{-i_0}^{(2)} = \frac{a_{-i} + b_{-i} - b_i}{c_2}$, so finally from Theorem \ref{theorem:a_fixed_t_i0}$(iv)$ we get
	\[t_{-i_0} = \sqrt{t_{-i_0}^{(1)} \cdot t_{-i_0}^{(2)}} = \frac{a_{-i} + b_{-i} - b_i}{\sqrt{c_1 c_2}}\]
\end{proof}
We have now gathered all necessary tools to start investigating step distribution functions.

@@

It therefore seems to make sense to discuss profit only within those intervals where the flow changes, or equivalently view profit with regard to flow intervals, since we ignore instances where the flow remains the same and thus there exists a $1-1$ relation between profit and flow.
It naturally follows that the best response of a link operator $i$ given $t_{-i}$ depends on the max profit value over any set of intervals that completely cover $[0, 1]$.
For step distribution functions, this set can be the domains of each of its finitely different values $\alpha_1 < \ldots < \alpha_m$.
As such $\forall k \in [m]$ we denote as $A_k$ the closed set of all players $p$ in $[0, 1]$ for whom $\alpha(p) = \alpha_k$.
Obviously $\cup_{k=1}^m A_k = [0, 1]$ and from the assumption that $\alpha$ is non-decreasing we also get $A_k$ convex $\forall k \in [m]$.
When looking at the flow (and consequently profit) of a specific link $i$, however, the split behaviour of the distribution function makes it possible for different flows having the same money sensitivity split.
We will therefore use the money sensitivity split function to refer to the respective flows that follow it, and formalise the profit and respective best response of link operator $i$ in the following definition.

When it comes to maximising profit for the pricing games, those values included in all $\Pi_{i, k}$ are all we need, because if $\as(t)$ takes any other in-between value, then we are on an instance where no player views the two link costs as equal, with players viewing a purely smaller cost in either link.
For the link operators, this means there at least one who can increase their toll and still keep the flow the same, achieving pure profit.
This can also happen in link cases of $\as(t) = \alpha_k$, so we move our full description of this behavior in the following lemma.

The most important corollary from that lemma comes from the fact that, as stated in \ref{lemma:a_fixed_ne}, for any $c > 0$ the flow for which the Nash Equilibrium emerges is always the same.
Consequently for any step function assigned to a pricing game with fixed latency functions, if a Nash Equilibrium exists then it needs to be on the same flow as the one emerging in the respective homogeneous pricing game.

With such a strong notion of the pricing Nash equilibrium, we can now see a potential algorithm that can be used to query its existence or not as well as calculate it.
We present it here.

@@

A natural extension of the above would be to examine them for $[N]$ parallel graphs.
Some of the properties naturally extend but for others more care is required.
Special notice and expansion is certainly necessary for the split function, as it is only defined for two links.
On a first thought, it seems trivial to also order the links on an equilibrium by latency and then define the split function on each consecutive pair, therefore also having an ordered set of split function values.
Still, more investigation is needed to uncover the relation between those values, and its consequences to the flow's or the pricing game's behaviours.

Putting the pricing games aside, it would also be interesting to expand the split function for series-parallel graphs.

@@

The standard technique to capture heterogeneity in the users of a network has been to apply a weight $\alpha$ to the toll cost viewed be each user, making their total cost $\ell(x) + \alpha t$.
This approach is equivalent to applying the inverse weight to the latency, i.e. make the cost $\tfrac1\alpha \ell(x) + t$.
Though less intuitive we already saw an application of this idea in Lemma \ref{lemma:heterogenous_flow_equiv_fixed} where we showed that a fixed distribution function is equivalent to restricting the latency functions inversely proportionally, however the idea could potentially be extended outside of fixed values.
This would of course does not guarantee that the latency functions will remain affine, or even polynomial.
One could attempt and investigate distribution functions that are inverse polynomials, making the respective latencies remain polynomial.
In any case we believe that a future work on the relation of the time-sensitivity with money sensitivity approaches, could uncover further insights in the behavior of heterogeneity.

@@

@@

\section*{Example calculations}

>>>>

\thispagestyle{empty}
\pagenumbering{gobble}

\chapter*{Συνοψη}
Σε αυτή τη διπλωματική μεταπτυχιακού μελετάμε ένα παίγνιο $2$ επιπέδων όπου, σε ένα δίκτυο με $n$ ακμές από μια πηγή $s$ σε ένα στόχο $t$, μια μονάδα ροής θέλει να μετακινηθεί από το $s$ στο $t$ χρησιμοποιώντας την ακμή με το χαμηλότερο κόστος, ενώ οι διαχειριστές των ακμών ανταγωνίζονται για κέρδος βάζοντας δίοδια στις ακμές και δημιουργώντας έτσι ένα παίγνιο συμφόρησης με διόδια.
Εξετάζουμε μόνο αφινικές καθυστερήσεις για τις ακμές.
Επιπλέον, ο κάθε χρήστης δικτύου αντιδρά στα διόδια με ετερογενή τρόπο, δηλ. ο κάθε παίκτης $p$ στη ροή του δικτύου έχει διαφορετική τιμή ευαισθησίας χρόνου-χρήματος, η οποία περιγράφεται από μια συνάρτηση κατανομής $\alpha(p)$.
Πρώτα παρουσιάζουμε κάποιους βασικούς ορισμούς και ιδιότητες των ομογενών παιγνίων κέρδους, κυρίως βασισμένα σε προηγούμενες δουλειές, και με αυτά ως βάση, τα επεκτείνουμε για να περιγράψουμε παίγνια κέρδους με ετερογενείς χρήστες.
Εισαγάγουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού ευαισθησίας $\as(t)$, ορισμένη για οποιεσδήποτε $2$ ακμές του δικτύου ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία, δωσμένων σετ διοδίων $t$, τα κόστη των $2$ ακμών είναι ίσα.
Με τη βοήθεια της $\as$ θα περιγράψουμε μερικές ιδιότητες γύρω από την εγωιστική συμπεριφορά των ετερογενών χρηστών για διαφορετικά διόδια, καθώς και θα αποδείξουμε την ύπαρξη άνω φράγματος για τις τιμές ευαισθησίας που αφορούν το παίγνιο.
Στη συνέχεια, φτάνοντας στο κύριο σώμα αυτής της έρευνας, εξετάζουμε την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών για διαφορετικές περιπτώσεις ετερογενών χρηστών.
Δείχνουμε ότι δεν υπάρχει ισορροπία Nash όταν υπάρχουν πολλοί χρήστες με $0$ ευαισθησία, δηλ. παίκτες που δεν επηρρεάζονται από τα διόδια, οπότε στο εξής υποθέτουμε ότι $\alpha(p) > 0$.
Κατόπιν εξετάζουμε περιπτώσεις όπου η συνάρτηση κατανομής είναι σταθερή, η οποίες, αν και δημιουργούν ομογενή συμπεριφορά στους χρήστες (κάνοντάς τα ψευδο-ετερογενή παίγνια), μας βοηθάνε να περιγράψουμε πώς συμπεριφέρονται η ροή, τα διόδια και τα σημεία ισορροπίας όταν αυτή η σταθερή τιμή μεταβάλλεται.
Χρησιμοποιώντας όλα τα παραπάνω, μελετάμε βηματικές συναρτήσεις κατανομής, όπου περιορίζοντας το μοντέλο μας σε στιγμιότυπα $2$ ακμών, παρουσιάζουμε αυστηρές συνθήκες αναγκαίες για την ύπαρξη ή μη σημείου ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών.
Παρουσιάζουμε και αναλύουμε έναν αλγόριθμο για τον υπολογισμό του σημείου ισορροπίας, αν υπάρχει, και κλείνουμε με μια συζήτηση για πιθανή μελοντική δουλειά.

@@

Acemoglu and Ozdaglar were the first to introduce pricing competition between link operators to the above model \cite{10.1287/moor.1060.0231}.
They showed that increasing the competition among operators from a monopoly to an oligopoly may reduce the efficiency of the network, achieving tight bounds on the Price of Anarchy.
In a follow-up work \cite{10.1109/JSAC.2007.070812}, they generalised the above by assuming more general topologies where links can also be linked serially (serial-parallel networks).
Correa et al. \cite{correa2018pricing} showed pricing games may not exist, may not be unique and can be arbitrarily inefficient, but regulating the network with toll caps can solve all three issues.
Harkes et al. \cite{Harks_2019} then showed that the same is true for uniform toll caps, which is stronger in practice as toll discrimination is often not allowed.
The latter two papers have also been main pillars of the current work.

@@

In this chapter we will introduce the pricing competition game to our model and examine how different distribution functions can affect the profit maximisation game between the toll operators.
We will begin by noticing that players with no toll fear, i.e. $\alpha(p)$ close to $0$, can be exploited by some link operators who then get unbounded profits (Lemma \ref{lemma:a_0_0}).
This obviously breaks the pricing competition game and, in turn, leads us to include the restriction of $\alpha(p) > 0$ when $p > 0$.
We will then proceed to analyse games with fixed distribution functions, where in Lemma \ref{lemma:a_fixed_homogeneous} we will show that such games are, as intuition suggests, equivalent to homogeneous games.
Special interest will then be on comparing such games, specifically those with the same setup but different fixed $\alpha$ functions, as Lemma \ref{lemma:a_fixed_c_relation} will reveal that, uniformly varying the player sensitivity, maps the toll values around the same flow.
The tools and notions built above will prove extremely useful when we next analyse games with step distribution functions, where we'll restrict our analysis to instances with $2$ links to simplify our work.
For those we will show an equivalence with a homogeneous game for a given toll \ref{lemma:heterogenous_flow_equiv_fixed} and combining it with Lemma \ref{lemma:alpha_step_gaps} where we'll show that a Nash Equilibrium cannot exist with all players of each sensitivity type using a single link, we get this chapter's main result, Theorem \ref{theorem:a_step_ne_equiv_fixed}, which states that if a Nash Equilibrium exists in a heterogeneous game with a step distribution function, then the respective homogeneous also has an equilibrium for the same set of tolls.
Using this notion, we will describe an algorithm (\ref{algorithm:step_ne_pricing}) which can decide existence and return the Nash Equilibrium for the pricing competition game in a heterogeneous $2$-link network.

@@

%What we need to examine  next is how those two games react differently for an link $i$ given a fixed $t_{-i}$.
%For this it is important to focus again on the fact that the flow is exclusively dependent on the toll difference.
We have now gathered all necessary tools to start investigating step distribution functions.

@@

With such a strong notion of the pricing Nash equilibrium, we can now see a potential algorithm that can be used to query its existence or not as well as calculate it.
We present it in Algorithm \ref{algorithm:step_ne_pricing}.

@@

In this chapter we will close on some of the discussions from previous chapters by exploring potential extensions of them that could be studied in future projects.

@@

For general heterogeneous models, the standard technique to capture the heterogeneity of the users in a network (at least in the accounted work) has been to apply a weight $\alpha$ to the toll cost viewed by each user, thus making their total cost $\ell(x) + \alpha t$.
This approach is equivalent to applying the inverse weight to the latency cost, i.e. make the cost $\tfrac1\alpha \ell(x) + t$.
We already saw an application of this idea in Lemma \ref{lemma:heterogenous_flow_equiv_fixed}, where we showed that a heterogeneous game with a fixed distribution function is equivalent to a homogeneous game with latency functions restricted inversely proportionally.
Unfortunately, as mentioned before, this correspondence is lost when considering non-fixed distribution functions, as then different tolls can create similar flows used by players with different sensitivity values, thus loosing the $1-1$ relation between latency and $\alpha$ values.

Still, we believe that studying games with time sensitivity costs instead of money sensitivity ones, i.e. heterogeneous games with user cost $\tfrac1\alpha \ell(x) + t$, has the potential to reveal more insights about the game's mechanics and heterogeneous behaviour, which can then be mapped back to game models with the standard user cost of $\ell(x) + \alpha t$.

@@

The following prepositions are not vetted and the author does not claim that any of the statements are concretely true.
They are included here, however, first to present some parallel results that were produced during the development of this research, and then to provide additional info in some of the discussions throughout.

@@

%To describe more properties of homogeneous pricing games we will need the following crucial Lemma.
\begin{lemma}
	\label{lemma:tolls_diff}
	Let $(N, \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$, a vector of $t_i - t_j$ values for all $t_j \in t_{-i}$.
	Then $D_i$ is decreasing with regard to any $t_j \in t_{-i}$.
\end{lemma}
